---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ftRtools
ftRtools is a package of internal FT Data Science tools for R. 

## Installation
To use the redshift query elements of this package you need [Java SE JDK][Java] 
installed. To install the package from Github use ```install_github``` function 
from the ```devtools``` package.

```{r, eval=FALSE}
devtools::install_github("Financial-Times/ftRtools")
```

## Credentials
To access FT Redshift you will need to use your credentials and be on the FT 
network. Do not hard code you username and password into files using these 
tools. Instead, use one of the available [alternatives][alternatives], two of
which are described below.

### .Renviron

One way to [save your credentials][credentials] is in a ```.Renviron``` file 
in your home directory and to include ```.Renviron``` in your ```.gitignore```. 
These variable can be accessed using ```Sys.getEnv()``` as follows:

```{r, eval=FALSE}
redshift_query("my_query.sql",
               "int",
               Sys.getenv("username"),
               Sys.getenv("password"))
```

For more information on the ```.Renviron``` file, see [here][Renviron]

### RStudio API

If you are working in RStudio, you can use the RStudio API as follows.

```{r, eval=FALSE}
redshift_query("my_query.sql",
               "int",
               rstudioapi::askForPassword("username"),
               rstudioapi::askForPassword("password"))
```

Bear in mind that if using this method, you will need to input your credentials
every time you run this code.

[credentials]: http://blog.revolutionanalytics.com/2015/11/how-to-store-and-use-authentication-details-with-r.html

[Java]: http://www.oracle.com/technetwork/java/javase/downloads/jdk8-downloads-2133151.html

[Renviron]: https://csgillespie.github.io/efficientR/r-startup.html#renviron

[alternatives]: https://db.rstudio.com/best-practices/managing-credentials/
