---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ftRtools
ftRtools is a package of internal FT Data Science tools for R. 

## Installation
To use the redshift query elements of this package you need [Java SE JDK](http://www.oracle.com/technetwork/java/javase/downloads/jdk8-downloads-2133151.html) installed. To install the package from github use ```install_github``` function from the ```devtools``` package.

```{r, eval=FALSE}
devtools::install_github("ftRtools")
```

## Examples
To access FT Redshift you will need to use your credentials and be on the FT network. Do not hard code you user name and password into files using these tools. Instead [save your credentials](http://blog.revolutionanalytics.com/2015/11/how-to-store-and-use-authentication-details-with-r.html) in a ```.Renviron``` file in your home directory and include ```.Renviron``` in your ```.gitignore```. These variable can be accessed using ```Sys.getEnv()``` as follows:

```{r, eval=FALSE}
redshift_query("my_query.sql",
               "int",
               Sys.getenv("username"),
               Sys.getenv("password"))
```
